\documentclass[12pt,twoside,a4paper]{article}
\usepackage{color}


\begin{document}
\title{\color{blue}The Building Blocks and Tools JavaScript Library.}
\author{F. Quinonez$^{1}$ and A. J. Hern\'{a}ndez G\'{o}ez$^{1}$\\
  \small{\em{1. CLEVER STATISTICS SAS, Barrancabermeja Colombia.}}
}
\maketitle
\begin{abstract}
Building Blocks and Tools (or simply BBTools) is a JavaScript library created 
to offer to its users a web based framework for si\-mu\-la\-ting, visualizing and analysing 
data across the web. BBTools is inspired by the three software most used in 
High Energy Physics and Biomedical Physics research, that are ROOT, GEANT4 and GATE; and rest
on another open source JavaScript libraries like D3, THREE and Requirejs. 
BBTools exploits the power of the modern web browsers and does not require installation as
its inspirers built with C++ do, so the users can start their analysis as soon as they download the library. 
BBTools due to be a web technology have a great potential to be a massive tool for any kind of users that want to work with data,
to boost learning and teaching Big-Data, to boost initiatives of Citizen Science and initiatives involving that the great Collaborations share their data, also to become a Mobile Application. 
BBTools Allow visualization in real time, not as GRID or batch systems like GISELA, lxplus, etc. etc. 
wherein users can not see visualization because the visualization
drivers are in the machines that are running the jobs. The main purpose of BBTools is to allow the users have a high quality and light weight visualization
plots and videos.
\end{abstract}

\end{document}
